Test of Adaptable User Interfaces

### 2015-07-07 paper.tex
Add testing context to Related Work

% =============================================================================
\section{Related Work}
% =============================================================================
TODO

>>>>

% =============================================================================
\section{Related Work}
% =============================================================================
Quality is very important in the software industry, and so are tests. They have been extensively studied by literature [TODO: some refs].
In a more modern context, Continuous Integration (CI) has been gaining popularity, hence is the need of automated tests.
An automated test is usually generated for the exact goal to achieve, then is executed and its results are compared to those expected, finally a report is constructed with a summary of the failures encountered. The report can be easily generated by IDE plugins as long as tests are well designed and use testing libraries (like JUnit). 
The increasing popularity of web-based softwares has obliged to develop tools to perform tests on these devices. Among them, are Selenium for browser-based applications, and Selendroid for Android applications.
Furthermore, GUIs have proven to be difficult to test, requiring new ways to verify them.
So automation of UI testing may be achieved by several means :
- using Finite State Machine-based modeling which suffers scaling problems [TODO: ref]
- creating an abstraction of the UI which is then tested in place of the UI itself [TODO: ref Sophie's paper]
- automated planning for hierarchical test case generation may be used which involves genetic algorithms [TODO: ref]
- using "capture and replay" method is rejected, as it would involve one capture per version [TODO: ref]
